\section{Installation}

So you decided to give Jhin3 a try? Great!
To run Jhin3, you need to have Java (version 8 or higher) installed. This makes Jhin3 compatible with all the major operating systems such as Linux, macOS and Windows. Jhin3 itself is nothing more than a jar file. This means that you can either install Jhin3 to a system directory or just put the jar file somewhere you like in your user directory. Decide for yourself what suits to your needs.

\subsection{Getting the jar file}

You can either download a pre-built version of Jhin3 from the GitHub releases page or you can build Jhin3 yourself.

\subsubsection{Downloading a pre-built version (recommended)}

Go to the GitHub releases page of Jhin3 (\href{https://github.com/hannesbraun/jhin3/releases}{or click here}). Select the latest version and download the associated zip file. It is called something like ``jhin3-2020.0.0.zip''.
Unpack the file and you will find the jar file inside.

\subsubsection{Building from source}

To build Jhin3 from source, make sure you have a JDK (version 8 or higher) installed as well as Maven.

Clone the Jhin3 repository to your computer and navigate to its root directory. Now, just run this command:
\begin{lstlisting}[language=bash]
mvn package
\end{lstlisting}

Inside of the target directory, you should find a file called ``jhin3-\{version\}-jar-with-dependencies.jar''.

\subsection{Optional: installing Jhin3}

Right now, you need to type
\begin{lstlisting}[language=bash]
java -jar /path/to/jhin3.jar
\end{lstlisting}
every time you want to run Jhin3. To simplify this, you can install Jhin3 to a system directory and execute it just by typing
\begin{lstlisting}[language=bash]
jhin3
\end{lstlisting}

\subsubsection{Linux/macOS}

In the /opt directory of your system, create a new directory called ``jhin3''. Rename the Jhin3 jar file to ``jhin3.jar'' and move it into this new directory.
Next, create a file called ``jhin3'' inside of ``/usr/local/bin''. This serves as a wrapper for the actual jar file.
Copy the following code inside that file:

\begin{lstlisting}[language=bash]
#!/bin/sh

java -jar /opt/jhin3/jhin3.jar "$@"
\end{lstlisting}

You should now be able to run Jhin3 anywhere by typing:
\begin{lstlisting}[language=bash]
jhin3
\end{lstlisting}

To update Jhin3, replace ``/opt/jhin3/jhin3.jar'' with the new jar file.
